|

### 2023-06-09 paper/article.qmd
reorganised project

---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  fig.path = "plots/"
)
source("../misc/functions.R")

```

@@

>>>>

---
title: |
    Whose voices are heard? [^1]

    [^1]: **Draft version. Please do not circulate or cite without permission.**
subtitle: "Making sense of framing patterns in protest coverage"
format:
  aft-pdf: default
  aft-html: default
author:
  - name: Johannes B. Gruber
    affiliations:
      - name: Vrije Universiteit Amsterdam
        department: Department of Communication Science
    orcid: 0000-0001-9177-1772
    email: j.b.gruber@vu.nl
    url: https://www.johannesbgruber.eu/
date: today
filters:
  - abstract-section
keywords: [protest paradigm, media framing, social movements, news reporting, content analysis]
reference-section-title: References
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  fig.path = "plots/"
)
source("../misc/functions.R")
```

# Abstract

```{r article, child = "abstract.md"}
```

# Protest Coverage

## The Protest Paradigm

@@

# Data and Methods

## Content Analysis

## Independent Variables

# Results

# Discussion and Conclusion
